Hierarchical Reverberation Mapping

### 2013-08-31 Paper/ms.tex
Writing, equations

There are deeper issues at play in reverberation mapping, for instance, the
mean lag $\tau$ is not the same as the mean radius of the BLR distribution,
and the mean lag $\tau$ is also not what the common cross-correlation
techniques measures. In this letter we will ignore these complications.

@@

\section{The Inference for a Single Object}
The posterior distribution for the lag of a single object $i$ is obtained
by fitting the following model.

\begin{eqnarray}
blah
\end{eqnarray}

Note that this is already not the cross-correlation.

The prior for the underlying time variation of the continuum emission is
a continuous autoregressive process of order 1, or a CAR(1) model. These models
have been studied extensively for AGN variability
\citep[e.g.][]{2009ApJ...698..895K, 2011ApJ...735...80Z, 2013ApJ...765..106Z}.

@@

>>>>

There are deeper issues at play in reverberation mapping, that we will ignore
for the purposes of this letter. We list them here for completeness. Firstly,
the mean lag $\tau$ is not equal to $c$ times the mean radius of the BLR
distribution. Secondly, the mean lag $\tau$ is also not what the common
cross-correlation techniques measures, except in the case of very narrow
transfer functions.

If the continuum light curve is described by a function $y(t)$, then the line
light curve $l(t)$ is given by
\begin{eqnarray}
l(t) &=& A \int_\tau \Psi(\tau)\left[y(t - \tau) - B\right] \, d\tau
\end{eqnarray}
where $\Psi(\tau)$ is the transfer function (assumed to be normalised),
and $A$ and $B$ are response
coefficients. The idea of reverberation mapping is to use noisy measurements
of $y(t)$ and $l(t)$ to infer the transfer function $\Psi(\tau)$ or a summary
of it such as the mean lag $\bar{\tau} = \int \tau\Psi(\tau) \, d\tau$.

@@

\section{The Single Object Model}
The posterior distribution for the mean lag $\bar{\tau}$ of a single object
$i$ is obtained
by fitting the following model. We assume, for simplicity, that
the transfer function is uniform
between limits $a$ and $b$, where $b > a$:
\begin{eqnarray}
\Psi(\tau) &=& \left\{
\begin{array}{lr}
\frac{1}{b-a}, & \tau \in [a,b]\\
0, & \textnormal{otherwise}s
\end{array}\right.
\end{eqnarray}
and our goal is to measure the mean lag $\bar{\tau} = \frac{1}{2}(b-a)$.

The prior for the underlying time variation of the continuum emission is
a continuous autoregressive process of order 1, or a CAR(1) model. These models
have been studied extensively for AGN variability
\citep[e.g.][]{2009ApJ...698..895K, 2011ApJ...735...80Z, 2013ApJ...765..106Z}.
Note that inferring $\bar{\tau}$ from the data requires that we
marginalise over an infinite number of nuisance parameters describing the
behaviour of $y(t)$ at unobserved times. This marginalisation can be done
either analytically or inside MCMC. We use the latter approach. We discretise
time using ten time bins per day, and have a discrete continuum light curve
$\mathbf{y} = \{y_1, ..., y_n\}$
\begin{eqnarray}
y_i = \mu + a\left(y_{i-1} - \mu\right) + \beta n_i
\end{eqnarray}
for $i \geq 2$, where the prior for the $\{n_i\}$ is independent standard
normal distributions. This is the discrete AR(1) model from time series theory.

@@

Note the single-object model is already an improvement over standard
cross-correlation techniques.
